Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2024-04-08 Edith Zemanick/Sweat Test/sweat_test_analysis.qmd
Update sweat_test_analysis.qmd

---
title: "Sweat electrolytes and CFTR activity in the era of CFTR modulators"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 10
    toc-float: true
    number-sections: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Documents/Notes/zotero.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(DiagrammeR)
library(readxl)
library(arsenal)
library(tidyverse)
library(factoextra)
library(pROC)
library(knitr)
library(caret)
source("/Users/timvigers/GitHub/CF/genotype_class_severity.R")
switch(Sys.info()[["sysname"]],
  Windows = {
    home_dir <- "C:/Users/timvigers/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Edith Zemanick/Sweat Test"
  },
  Darwin = {
    home_dir <- "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Edith Zemanick/Sweat Test"
  }
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

plot(roc_cf, print.auc = TRUE, col = "blue")
plot(roc_non_cf, print.auc = TRUE, col = "red")
```

>>>>

---
title: "Sweat electrolytes and CFTR activity in the era of CFTR modulators"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 10
    toc-float: true
    number-sections: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
editor: source
---

```{r setup}
#| include: false
library(DiagrammeR)
library(readxl)
library(arsenal)
library(tidyverse)
library(factoextra)
library(pROC)
library(knitr)
library(caret)
source("~/GitHub/CF/genotype_class_severity.R")
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Edith Zemanick/Sweat Test",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Edith Zemanick/Sweat Test",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Edith Zemanick/Sweat Test"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

plot(roc_cf, print.auc = TRUE,lty=1)
plot(roc_non_cf, print.auc = TRUE,add=T,lty=2,print.auc.y=0.4)
legend("bottomright",legend = c("CF vs. CFTR-RD or CRMS","Non-CF vs. CFTR-RD or CRMS"),lty = c(1,2))
```
